Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-15 paper/paper.tex
nudges

In recent years the development of program synthesis has found many ways to
obtain correct by design programs from high-level specifications.  One such
approach~\cite{itzhaky2010simple} looks to inductively synthesize invariants
to generate the desired programs.  Since these digital programs are already
constrained by designed to factors such as FWL, these approaches are ideal
for the synthesis of parametric controllers. 
In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the
synthesis of switching controllers for stabilizing continuous-time plants
with polynomial dynamics.  The work extends to its application on affine
systems, finding its major challenge in the hardness of solving linear
arithmetic on present SMT solvers.  Since this approach uses switching
states instead of linear dynamics in the digital controller, it entirely
circumvents the FWL problem.  It is also not suitable for the kind of
control we seek to synthesize.  What is needed in this regard is the
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
while enhancing the procedure by evaluating the quantization effects of
the Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
representation of the continuous dynamics.

@@

We have presented a CEGIS-based approach implemented in a tool called \tool, 
which uses inductive synthesis in conjunction with an algorithm for verifying 
robust closed-loop stability. In particular, \tool is able to compute a parametric solution 
for a stabilizing digital controller given a continuous (or discrete) plant 
specification.  This enables us to automatically synthesize correct-by-construction 
digital controllers for a given model of their physical environment.  
Our approach addresses the effects of the quantizers (A/D and D/A converters) 
as time discretization elements with quantization noise.  Our experimental results 
show that \tool is able to synthesize stable controllers in most benchmarks within
reasonable time frames fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
%
Future work will be the extension of this CEGIS-based approach to further
classes of systems, including state-space representation.  
We will also consider performance requirements while
synthesizing the digital controller.

>>>>

Program synthesis is the problem of computing correct-by-design programs
from high-level specifications, and algorithms for this problem have made
substantial progress in recent years.  One such
approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
generate the desired programs.

Program synthesisers are an ideal fit for synthesis of parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesize.  We require a
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from~\cite{daes20161}
while enhancing the procedure by evaluating the quantization effects of the
Hardware interfaces (ADC/DAC) to obtain an accurate discrete-time FWL
representation of the continuous dynamics.

@@

We have presented a CEGIS-based approach implemented in a tool called \tool,
which uses inductive synthesis in conjunction with an algorithm for
verifying robust closed-loop stability.  In particular, \tool is able to
compute a parametric solution for a stabilizing digital controller given a
continuous (or discrete) plant specification.  This enables us to
automatically synthesize correct-by-construction digital controllers for a
given model of their physical environment.  Our approach addresses the
effects of the quantizers (A/D and D/A converters) as time discretization
elements with quantization noise.  Our experimental results show that \tool
is able to synthesize stable controllers in most benchmarks within
a reasonable amount of time fully automatically.
%
% and can be 
%complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
%Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.

Future work will be the extension of this CEGIS-based approach to further
classes of systems, including state-space representation.  We will also
consider performance requirements while synthesizing the digital controller.
